KidsAIR initial SUMs data work

### 2020-01-07 sums_data_cleaning.Rmd
SUMs cleaning

---
title: "KidsAIR initial SUMs data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 3 Jan 2020"
output: pdf_document
---

@@

>>>>

---
title: "KidsAIR initial SUMs data work"
author: "Ethan Walker"
date: "Started 23 Dec 2019, Updated 6 Jan 2020"
output: pdf_document
---

@@

# Compile start and stop times for SUMs based on field logs
```{r}
# Load all SUMs data
all_sums_raw <- read_rds("Output/all_sums_raw.rds") %>% 
  ungroup() %>% 
  arrange(area, home, datetime_sums)

# Load and format SUMs data logs for WMT
wmt_sums_log <- read_rds("Output/wmt_sums_data_log.rds")

wmt_sums_stop <- read_csv("Input/WMT/wmt_medicalvisit_20200107.csv") %>% 
  mutate(home_winter_id = HomeWinterID,
         final_visit_date = if_else(VisitDate == "11/4/2025", "11/4/2015", VisitDate),
         final_visit_date = mdy(final_visit_date)) %>% 
  group_by(home_winter_id) %>% 
  arrange(final_visit_date) %>% 
  mutate(date_last = last(final_visit_date),
         date_filter = if_else(date_last == final_visit_date, 1, 0)) %>% 
  ungroup() %>% 
  filter(date_filter == 1) %>% 
  select(home_winter_id, final_visit_date) %>% 
  distinct(.keep_all = TRUE) %>% 
  arrange(home_winter_id) %>% 
  mutate(time = "01:00:00") %>% 
  unite(datetime_stop, c("final_visit_date", "time"), sep = " ") %>% 
  mutate(datetime_stop = ymd_hms(datetime_stop))

wmt_sums_start <- read_xlsx("Input/WMT/wmt_sums_start_times_20200107.xlsx") %>% 
  mutate(datetime_start = ymd_hms(datetime_start))

wmt_sums_start_stop <- wmt_sums_start %>% 
  left_join(wmt_sums_stop, by = "home_winter_id")

wmt_sums_raw <- all_sums_raw %>% 
  filter(area == "WMT") %>% 
  left_join(wmt_sums_start_stop, by = c("area", "home")) %>% 
  mutate(filter_var = 
         if_else(datetime_sums > datetime_start & datetime_sums < datetime_stop,
                 1, 0))

wmt_sums_filtered <- wmt_sums_raw %>% 
  filter(filter_var == 1) %>% 
  arrange(area, home, winter_id, datetime_sums)

# Start here next:
## Make sure datetime_sums lines up with start/stop range
## Work on cleaning up temp_c_sums
## Ask about NN/AK finish dates and move on to repeating steps for those homes
write_rds(wmt_sums_filtered, "Output/wmt_sums_filtered.rds")

nn_sums_log <- read_rds("Output/nn_sums_data_log.rds")
# Need to get the NN medicalvisit file once data collection is finished
nn_sums_stop <- read_csv("Input/NN/nn_medicalvisit_20200107.csv") %>% 
  mutate(home_winter_id = HomeWinterID,
         final_visit_date = if_else(VisitDate == "11/4/2025", "11/4/2015", VisitDate),
         final_visit_date = mdy(final_visit_date)) %>% 
  group_by(home_winter_id) %>% 
  arrange(final_visit_date) %>% 
  mutate(date_last = last(final_visit_date),
         date_filter = if_else(date_last == final_visit_date, 1, 0)) %>% 
  ungroup() %>% 
  filter(date_filter == 1) %>% 
  select(home_winter_id, final_visit_date) %>% 
  distinct(.keep_all = TRUE) %>% 
  arrange(home_winter_id)

ak_sums_log <- read_rds("Output/ak_sums_data_log.rds")
# Need to get the AK medicalvisit file once data collection is finished
ak_sums_stop <- read_csv("Input/AK/ak_medicalvisit_20200107.csv") %>% 
  mutate(home_winter_id = HomeWinterID,
         final_visit_date = if_else(VisitDate == "11/4/2025", "11/4/2015", VisitDate),
         final_visit_date = mdy(final_visit_date)) %>% 
  group_by(home_winter_id) %>% 
  arrange(final_visit_date) %>% 
  mutate(date_last = last(final_visit_date),
         date_filter = if_else(date_last == final_visit_date, 1, 0)) %>% 
  ungroup() %>% 
  filter(date_filter == 1) %>% 
  select(home_winter_id, final_visit_date) %>% 
  distinct(.keep_all = TRUE) %>% 
  arrange(home_winter_id)
```
